\chapter{Conclusion and Key Insights}

The practical implementations demonstrated distinct strengths for each database type. MongoDB excelled at complex aggregations with 50 student documents, achieving sub-second response times for nested data queries. Cassandra's partition strategy efficiently processed 22 attendance records with linear scalability for time-series data. Neo4j's graph traversal revealed complex relationships between 13 nodes and 12 relationships using natural pattern matching. Redis achieved sub-millisecond response times for 1000+ atomic operations, making it ideal for real-time session management and caching. CockroachDB maintained ACID properties across 10 concurrent banking transactions, providing financial-grade consistency in a distributed environment.

The key insight is that modern applications benefit from using multiple database types, each optimized for specific query patterns. MongoDB's aggregation pipelines handle complex analysis efficiently, Cassandra's partition strategy scales time-series data linearly, Neo4j's graph traversal reveals hidden relationships naturally, Redis's atomic operations provide unmatched speed for real-time operations, and CockroachDB's distributed transactions maintain ACID properties across nodes. Successful database architecture requires matching query patterns to database strengths and implementing hybrid solutions that leverage the unique capabilities of each database type.

\begin{table}[H]
\centering
\begin{tabular}{|l|c|c|c|}
\hline
\textbf{Database} & \textbf{Query Type} & \textbf{Data Volume} & \textbf{Performance} \\
\hline
\texttt{MongoDB} & \texttt{Complex aggregation} & \texttt{50} documents & \texttt{Sub-second} \\
\texttt{Cassandra} & \texttt{Time-series query} & \texttt{22} records & \texttt{Linear scale} \\
\texttt{Neo4j} & \texttt{Graph traversal} & \texttt{13} nodes & \texttt{Fast pattern} \\
\texttt{Redis} & \texttt{Atomic operations} & \texttt{1000+} ops & \texttt{Sub-ms} \\
\texttt{CockroachDB} & \texttt{ACID transactions} & \texttt{10} concurrent & \texttt{Strong consistency} \\
\hline
\end{tabular}
\caption{Performance Comparison Summary}
\label{tab:performance-summary}
\end{table}